Tulai

### 2023-09-12 paper/scraps/scraps-tulai.qmd
organise the scraps a bit

---
title: "Tulai"
author: ""
date: now
format: 
  html:
    self-contained: true
execute: 
  warning: false
  fig-dpi: 600
title-block-published: "last updated"
editor: visual
---

>>>>

---
title: ""
author: ""
date: now
format: 
  html:
    self-contained: true
execute: 
  warning: false
  fig-dpi: 600
title-block-published: "last updated"
editor: visual
---
